---
title: "431 Project A Proposal Template"
author: "Your Name (or Names) Should Be Here"
date: last-modified
format: 
  html:
    toc: true
    number-sections: true
    date-format: iso
    embed-resources: true
    code-overflow: wrap
    theme: default
---

# R Packages

```{r}
#| message: false

library(Hmisc)
library(janitor)
library(naniar)
library(sessioninfo)

# if you wish to add other packages, do so here

library(tidyverse)

knitr::opts_chunk$set(comment = NA)
```

# Data Ingest

```{r}
data_url <- 
  "https://www.countyhealthrankings.org/sites/default/files/media/document/analytic_data2023_0.csv"

chr_2023_raw <- read_csv(data_url, skip = 1, guess_max = 4000,
                         show_col_types = FALSE)
```

# State Selection

# Variable Selection

# Variable Cleaning and Renaming

# Creating the Analysis 2 Predictor

# Arranging and Saving the Analytic Tibble

# Print the Tibble

# Numerical Summaries

# The Codebook

Our **add name of tibble** tibble contains *add code* counties and *add code* variables.

Variable | Original | Role | NA | Distinct | Definition
:------: | :-------: | :-----: | ---: | -----: | ----------------------------------
**fipscode** | -- | ID | *add code* | *add code* | county's FIPS code
**state** | -- | ID | *add code* | *add code* | state postal abbreviation
**county** | -- | ID | *add code* | *add code* | county name
add other 6 variables | - | - | - | - | - 
**county_ranked** | -- | Check | *add code* | *add code* | *be sure that* all values are 1

# Research Question for Analysis 1

# Research Question for Analysis 2

# Reflection

# Session Information

```{r}
session_info()
```

