---
title: "431 Project A Portfolio Report Template"
author: "Your Name (or Names) Should Be Here"
date: last-modified
format: 
  html:
    toc: true
    number-sections: true
    date-format: iso
    embed-resources: true
    code-overflow: wrap
    theme: default
---

:::{.callout-tip title="Read the Sample Proposal"}

You will get more out of this template if you work with it in combination with the **431 Project A Sample Portfolio Report**, which provides more detail for each section of the Portfolio. 

See the [Project A Examples](https://thomaselove.github.io/431-projectA-2023/examples.html) for more details and useful links.

*Be certain* to delete this note when you submit your final portfolio, along with my other instructions.

:::

# R Packages

:::{.callout-tip title="Delete these instructions when submitting your work"}

Follow the instructions for this section found in the R Packages section of the [Proposal page](https://thomaselove.github.io/431-projectA-2023/proposal.html).

Leave in the code below, augmenting it with additional packages as necessary, where indicated.

:::

```{r}
#| message: false

library(Hmisc)
library(janitor)
library(naniar)
library(xfun) ## or, if you prefer use library(sessioninfo)

# if you wish to add other packages, do so here

library(tidyverse)

knitr::opts_chunk$set(comment = NA)
```

# Data Ingest

:::{.callout-tip title="Delete these instructions when submitting your work"}

Follow the instructions for this section found in Data Task 1 on the [Data page](https://thomaselove.github.io/431-projectA-2023/data.html), as well as the Data Ingest section of the [Proposal page](https://thomaselove.github.io/431-projectA-2023/proposal.html).

A little bit of important code is included below.

:::

```{r}
data_url <- 
  "https://www.countyhealthrankings.org/sites/default/files/media/document/analytic_data2023_0.csv"

chr_2023_raw <- read_csv(data_url, skip = 1, guess_max = 4000,
                         show_col_types = FALSE)
```

# State Selection

:::{.callout-tip title="Delete these instructions when submitting your work"}

Follow the instructions for this section found in Data Task 2 on the [Data page](https://thomaselove.github.io/431-projectA-2023/data.html), as well as the State Selection section of the [Proposal page](https://thomaselove.github.io/431-projectA-2023/proposal.html).

:::

# Variable Selection

:::{.callout-tip title="Delete these instructions when submitting your work"}

Follow the instructions for this section found in Data Task 3 on the [Data page](https://thomaselove.github.io/431-projectA-2023/data.html), as well as the Variable Selection section of the [Proposal page](https://thomaselove.github.io/431-projectA-2023/proposal.html).


:::

# Variable Cleaning and Renaming

:::{.callout-tip title="Delete these instructions when submitting your work"}

Follow the instructions for this section found at the end of Data Task 3 on the [Data page](https://thomaselove.github.io/431-projectA-2023/data.html), as well as the Variable Cleaning and Renaming section of the [Proposal page](https://thomaselove.github.io/431-projectA-2023/proposal.html).
.

:::

# Creating the Analysis 2 Predictor

:::{.callout-tip title="Delete these instructions when submitting your work"}

Follow the instructions for this section found in Data Task 4 on the [Data page](https://thomaselove.github.io/431-projectA-2023/data.html), as well as the Creating the Analysis 2 Predictor section of the [Proposal page](https://thomaselove.github.io/431-projectA-2023/proposal.html).
.

:::

# Adding 2018 Data for the Analysis 3 Outcome

:::{.callout-tip title="Delete these instructions when submitting your work"}

Follow the instructions for this section found in Data Task 5 on the [Data page](https://thomaselove.github.io/431-projectA-2023/data.html), as well as the Adding 2018 Data for the Analysis 3 Outcome section of the [Proposal page](https://thomaselove.github.io/431-projectA-2023/proposal.html).

:::

# Arranging and Saving the Analytic Tibble

:::{.callout-tip title="Delete these instructions when submitting your work"}

Follow the instructions for this section found in Data Task 6 on the [Data page](https://thomaselove.github.io/431-projectA-2023/data.html), as well as the Arranging and Saving the Analytic Tibble section of the [Proposal page](https://thomaselove.github.io/431-projectA-2023/proposal.html).

:::

# Print the Tibble

:::{.callout-tip title="Delete these instructions when submitting your work"}

Follow the relevant instructions for this section found on the [Proposal page](https://thomaselove.github.io/431-projectA-2023/proposal.html).

:::


# Numerical Summaries

:::{.callout-tip title="Delete these instructions when submitting your work"}

Follow the relevant instructions for this section found on the [Proposal page](https://thomaselove.github.io/431-projectA-2023/proposal.html).

:::

# The Codebook

:::{.callout-tip title="Delete these instructions when submitting your work"}

Follow the relevant instructions for this section found on the [Proposal page](https://thomaselove.github.io/431-projectA-2023/proposal.html).

:::

Our **add name of tibble** tibble contains *add code* counties and *add code* variables.

Variable | Original | Role | NA | Distinct | Definition
:------: | :-------: | :-----: | ---: | -----: | ----------------------------------
**fipscode** | -- | ID | *add code* | *add code* | county's FIPS code
**state** | -- | ID | *add code* | *add code* | state postal abbreviation
**county** | -- | ID | *add code* | *add code* | county name
add other selected variables | - | - | - | - | - 
**county_ranked** | -- | Check | *add code* | *add code* | *be sure that* all values are 1

**Missingness Check** goes here.

**Distinct Values Check** goes here.

# Research Questions

:::{.callout-tip title="Delete these instructions when submitting your work"}

Follow the relevant instructions for this section, and its subsections, found on the [Proposal page](https://thomaselove.github.io/431-projectA-2023/proposal.html).

:::

## Analysis 1 Research Question

## Analysis 2 Research Question

## Analysis 3 Research Question

# Analysis 1

:::{.callout-tip title="Delete these instructions when submitting your work"}

Follow the instructions on the [Analyses page](https://thomaselove.github.io/431-projectA-2023/analyses.html) carefully.

:::

## Variables

## Summaries

## Approach

## Conclusions

# Analysis 2

:::{.callout-tip title="Delete these instructions when submitting your work"}

Follow the instructions on the [Analyses page](https://thomaselove.github.io/431-projectA-2023/analyses.html) carefully.

:::

## Variables

## Summaries

## Approach

## Conclusions

# Analysis 3

:::{.callout-tip title="Delete these instructions when submitting your work"}

Follow the instructions on the [Analyses page](https://thomaselove.github.io/431-projectA-2023/analyses.html) carefully.

:::

## Variables

## Summaries

## Approach

## Conclusions

# Portfolio Reflections

:::{.callout-tip title="Delete these instructions when submitting your work"}

The original "Proposal Reflections" section is only included as Section 13 in the Proposal, and should not be included in the final portfolio report. Instead, write a new paragraph (containing at least four well-constructed complete English sentences) to answer the following question:

What was the most important thing you learned as a result of doing this project, and why?

:::


# Session Information

```{r}
session_info()
```

