---
title: "431 Project A Proposal Template"
author: "Your Name (or Names) Should Be Here"
date: last-modified
format: 
  html:
    toc: true
    number-sections: true
    date-format: iso
    embed-resources: true
    code-overflow: wrap
    theme: default
---

:::{.callout-tip title="Read the Sample Proposal"}

You will get more out of this template if you work with it in combination with the **431 Project A Sample Proposal**, which provides more detail for each section of the Proposal. 

See the [Project A Examples](https://thomaselove.github.io/431-projectA-2023/examples.html) for more details and useful links.

*Be certain* to delete this note when you submit your final proposal, along with my other instructions.

:::

# R Packages

:::{.callout-tip title="Delete these instructions when submitting your work"}

Follow the instructions for this section found in the R Packages section of the [Proposal page](https://thomaselove.github.io/431-projectA-2023/proposal.html).

Leave in the code below, augmenting it with additional packages as necessary, where indicated.

:::

```{r}
#| message: false

library(Hmisc)
library(janitor)
library(naniar)
library(sessioninfo)

# if you wish to add other packages, do so here

library(tidyverse)

knitr::opts_chunk$set(comment = NA)
```

# Data Ingest

:::{.callout-tip title="Delete these instructions when submitting your work"}

Follow the instructions for this section found in Data Task 1 on the [Data page](https://thomaselove.github.io/431-projectA-2023/data.html), as well as the Data Ingest section of the [Proposal page](https://thomaselove.github.io/431-projectA-2023/proposal.html).

A little bit of important code is included below.

:::

```{r}
data_url <- 
  "https://www.countyhealthrankings.org/sites/default/files/media/document/analytic_data2023_0.csv"

chr_2023_raw <- read_csv(data_url, skip = 1, guess_max = 4000,
                         show_col_types = FALSE)
```

# State Selection

:::{.callout-tip title="Delete these instructions when submitting your work"}

Follow the instructions for this section found in Data Task 2 on the [Data page](https://thomaselove.github.io/431-projectA-2023/data.html), as well as the State Selection section of the [Proposal page](https://thomaselove.github.io/431-projectA-2023/proposal.html).

:::

# Variable Selection

:::{.callout-tip title="Delete these instructions when submitting your work"}

Follow the instructions for this section found in Data Task 3 on the [Data page](https://thomaselove.github.io/431-projectA-2023/data.html), as well as the Variable Selection section of the [Proposal page](https://thomaselove.github.io/431-projectA-2023/proposal.html).


:::

# Variable Cleaning and Renaming

:::{.callout-tip title="Delete these instructions when submitting your work"}

Follow the instructions for this section found at the end of Data Task 3 on the [Data page](https://thomaselove.github.io/431-projectA-2023/data.html), as well as the Variable Cleaning and Renaming section of the [Proposal page](https://thomaselove.github.io/431-projectA-2023/proposal.html).
.

:::

# Creating the Analysis 2 Predictor

:::{.callout-tip title="Delete these instructions when submitting your work"}

Follow the instructions for this section found in Data Task 4 on the [Data page](https://thomaselove.github.io/431-projectA-2023/data.html), as well as the Creating the Analysis 2 Predictor section of the [Proposal page](https://thomaselove.github.io/431-projectA-2023/proposal.html).
.

:::

# Adding 2018 Data for the Analysis 3 Outcome

:::{.callout-tip title="Delete these instructions when submitting your work"}

Follow the instructions for this section found in Data Task 5 on the [Data page](https://thomaselove.github.io/431-projectA-2023/data.html), as well as the Adding 2018 Data for the Analysis 3 Outcome section of the [Proposal page](https://thomaselove.github.io/431-projectA-2023/proposal.html).

:::

# Arranging and Saving the Analytic Tibble

:::{.callout-tip title="Delete these instructions when submitting your work"}

Follow the instructions for this section found in Data Task 6 on the [Data page](https://thomaselove.github.io/431-projectA-2023/data.html), as well as the Arranging and Saving the Analytic Tibble section of the [Proposal page](https://thomaselove.github.io/431-projectA-2023/proposal.html).

:::

# Print the Tibble

:::{.callout-tip title="Delete these instructions when submitting your work"}

Follow the relevant instructions for this section found on the [Proposal page](https://thomaselove.github.io/431-projectA-2023/proposal.html).

:::


# Numerical Summaries

:::{.callout-tip title="Delete these instructions when submitting your work"}

Follow the relevant instructions for this section found on the [Proposal page](https://thomaselove.github.io/431-projectA-2023/proposal.html).

:::

# The Codebook

:::{.callout-tip title="Delete these instructions when submitting your work"}

Follow the relevant instructions for this section found on the [Proposal page](https://thomaselove.github.io/431-projectA-2023/proposal.html).

:::

Our **add name of tibble** tibble contains *add code* counties and *add code* variables.

Variable | Original | Role | NA | Distinct | Definition
:------: | :-------: | :-----: | ---: | -----: | ----------------------------------
**fipscode** | -- | ID | *add code* | *add code* | county's FIPS code
**state** | -- | ID | *add code* | *add code* | state postal abbreviation
**county** | -- | ID | *add code* | *add code* | county name
add other selected variables | - | - | - | - | - 
**county_ranked** | -- | Check | *add code* | *add code* | *be sure that* all values are 1

**Missingness Check** goes here.

**Distinct Values Check** goes here.

# Research Questions

:::{.callout-tip title="Delete these instructions when submitting your work"}

Follow the relevant instructions for this section, and its subsections, found on the [Proposal page](https://thomaselove.github.io/431-projectA-2023/proposal.html).

:::

## Analysis 1 Research Question

## Analysis 2 Research Question

## Analysis 3 Research Question

# Proposal Reflection

:::{.callout-tip title="Delete these instructions when submitting your work"}

Here you will provide a paragraph describing the most challenging (or difficult) part of completing the work so far, and how you were able to overcome whatever it was that was most challenging.

Your discussion of the biggest challenge includes a paragraph (or more) written in English, with attention paid to grammar, syntax and spelling. It needs to be clear to us from reading your reflection what your biggest issue was, and how you tried to address it.

:::

# Session Information

```{r}
session_info()
```

