---
title: "431 Lab 03"
author: "Your Name Goes Here"
date: last-modified
format: 
  html:
    toc: true
    number-sections: true
    embed-resources: true
    date-format: iso
    theme: paper
    highlight: textmate
---

## Setup

```{r, message = FALSE, warning = FALSE}
library(palmerpenguins)
library(tidyverse)

## always need tidyverse, can include other packages too
## which should always be inserted above the tidyverse
## need palmerpenguins for Questions 1-3

theme_set(theme_light())  # or use theme_set(theme_bw())
knitr::opts_chunk$set(comment=NA)
```

## Import the `lab03-data.csv` data 

You'll need to do this on your own. Use the ideas from Lab 02 and the instructions from Labs 02 and 03 to help you. 

## First Steps

Make sure you have changed the title and author of this, back in the YAML section at the very top of this file, and make sure you change this file's name by inserting your actual name, rather than just calling it `431-lab03-template-2023.qmd`. Make the document as attractive as you can. Finally, make sure you have deleted all of the instructions, including these before you submit your final work.

# Question 1

Begin typing your answer to Question 1 here. Use complete sentences.

If you need to build some code to answer a question, create a chunk of code like the one below, which looks at bill lengths by species rather than our area of interest, and also ignores the missing data, creating a warning. This plot is also not very attractive, and not labeled effectively. 

```{r q01_box}
ggplot(penguins, aes(x = species, y = bill_length_mm)) +
  geom_boxplot()
```

# Question 2

Here's where you should type in your answer to Question 2. You should include the code you use to obtain the summaries of interest. Here's an approach that yields the mean of the bill lengths after trimming away the missing data, and also the highest 10% and the lowest 10% of the non-missing data. Of course, this particular summary is also not useful to us directly.

```{r q02_trimmed_mean_bill_length}
mean(penguins$bill_length_mm, trim = 0.1, na.rm = TRUE)
```

# Question 3

Your answer to Question 3 goes here. You will need to display your code and the resulting plot, as well.

# Question 4

Answer to Question 4 goes here. The `slice_sample()` function should be helpful. Remember to precede your sampling with the code:

```{r}
set.seed(1)
```

# Question 5

Answer to Question 5 goes here.

# Question 6

Replace this text with your response to Question 6.

# Session Information

```{r}
sessioninfo::session_info()
```
