---
title: "431 Lab 1 Template (Replace this name)"
author: "(Your Name Goes Here)"
date: last-modified
format: 
  html:
    toc: true
    number-sections: true
    embed-resources: true
    date-format: iso
    theme: materia
---

:::{.callout-important}

Delete **all of the instructions** we provide to you in this template, in favor of your own words, before submitting your work. You are welcome to retain any or all of the R code we provide in this template as part of your response.

:::

## R Setup {.unnumbered}

```{r}
#| message: false

library(knitr)
library(naniar)

## add additional packages here, as needed

library(easystats)
library(tidyverse)
```

# Task 1

Here is the heading of the data file, as shown in the instructions.

```{r}
cms_patient_experience |> head()
```

Here is the place to put your numerical summary.




Write your complete English sentences here.

If you need a second paragraph, place it here, with a blank line between paragraphs.


# Task 2

Place your R code here.

Write your interpretation here.

# Task 3

Place your R code to build your plot here.

Your interpretation goes here.

# Task 4

Here is the code to create the subset of interest, from our instructions:

```{r}
task4dat <- cms_patient_experience |>
  filter(measure_cd == "CAHPS_GRP_2" | measure_cd == "CAHPS_GRP_8") |>
  pivot_wider(names_from = c(measure_cd, measure_title),
              values_from = prf_rate) |>
  rename("Communicate" = "CAHPS_GRP_2_CAHPS for MIPS SSM: How Well Providers Communicate",
         "Staff" = "CAHPS_GRP_8_CAHPS for MIPS SSM: Courteous and Helpful Office Staff") |>
  drop_na()

head(task4dat)
```

Here is the code for the original plot, which you will need to modify appropriately:

```{r}
ggplot(task4dat, aes(x = Staff, y = Communicate)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ x, se = TRUE, col = "red") +
  theme_bw()
```

Here would be a good place to provide R code to identify the slope and intercept of the fitted line.

Your interpretation of that slope and intercept should go here.

# Task 5

This will be the video. No need to write anything about it here, except to specify the name of the file, which should ideally be ...

`yourname-431lab1.mp4`

# Session Information

Use the code below to include your session information.

```{r}
xfun::session_info()
```
