---
title: "Code used in Class 03"
author: "Thomas E. Love, Ph.D."
date: last-modified
format: 
  html:
    toc: TRUE
    number-sections: true
    date-format: iso
    embed-resources: true
---

# Data Ingest

## Load R Packages

```{r library_load, message = FALSE}

## add additional libraries/packages here, as needed

library(janitor)
library(patchwork)
library(easystats)
library(tidyverse) # always load tidyverse last

theme_set(theme_bw())  ## or use theme_set(theme_light())
knitr::opts_chunk$set(comment = NA)
```

## Load Data

Our data come from the [Quick 15-item Survey](https://github.com/THOMASELOVE/431-classes-2025/blob/main/class02/431_surveyhandout_1perstudent_2025-09-04.pdf) we did in Class 02, and which we’ve done (in various forms) since 2014.

```{r load_data}
## Note: I have the quick_survey_2024.csv file stored in  
## subfolder called data under my Class 03 project

url_raw <- "https://raw.githubusercontent.com/THOMASELOVE/431-data/refs/heads/main/data/survey15_2014_to_2025.csv"

surv15_raw <- 
  read_csv(url_raw, show_col_types = FALSE) |>
  janitor::clean_names()
```

## Result

```{r}
surv15_raw
```

## A more detailed look?

```{r}
glimpse(surv15_raw)
```

# Six Key Verbs

## `filter()`

```{r}
surv15_raw |> filter(year == "2025")
```

## `select()`

```{r}
surv15_raw |> select(student, glasses, lastsleep)
```

## `arrange()`

```{r}
surv15_raw |> arrange(height_in) |> 
  select(student, height_in)
```

## `mutate()`

```{r}
surv15_raw |> select(student, love_htcm, lovetrueht) |>
  mutate(ht_error = love_htcm - lovetrueht)
```

## `group_by()` and `summarize()`

```{r}
surv15_raw |> 
  filter(complete.cases(height_in), year > 2018) |> 
  group_by(year) |> summarize(n(), median(height_in)) 
```

# Some Counting and Summarizing

## Counting the `glasses` variable

```{r}
surv15_raw |> count(glasses)
```

## Counting `glasses` and `english`

```{r}
surv15_raw |> count(glasses, english)
```

## Favorite Color in 2025?

```{r}
surv15_raw |>
    filter(year == "2025") |>
    tabyl(favcolor) |>
    adorn_pct_formatting()
```

## Using `summary()` on Quantities

```{r}
surv15_raw |> 
  select(love_htcm, haircut, height_in, lastsleep) |>
  summary()
```

## More Descriptive Summaries

```{r}
surv15_raw |>
  select(love_htcm, haircut, height_in, lastsleep) |>
  describe_distribution()
```

## Even More Descriptive Summaries

```{r}
surv15_raw |>
  select(love_htcm, haircut, height_in, lastsleep) |>
  describe_distribution(centrality = "median")
```

# Manage the data into an analytic tibble called `surv15`

## Select our variables

```{r}
surv15 <- surv15_raw |>
    select(student, year, english, smoke, 
           pulse, height_in, haircut)
```

## What do we have now?

```{r}
dim(surv15)
surv15
```

## Initial Numeric Summaries

```{r}
summary(surv15)
```

```{r}
names(surv15)
```

## Categorical variables as factors

```{r}
#| echo: true
surv15 <- surv15 |>
    mutate(year = as_factor(year),
           smoke = as_factor(smoke),
           english = as_factor(english),
           student = as.character(student))
```

## Now, how's our summary?

```{r}
summary(surv15)
```

```{r}
surv15 |> tabyl(year) |> adorn_totals() |> adorn_pct_formatting()
```

# Three Exploratory Questions

## Three Exploratory Questions

1. What is the distribution of pulse rates among students in 431 since 2014?
2. Does the distribution of student heights change materially over time?
3. Is the Normal distribution a good model for student heights? How about for student haircut prices?

# Question 1

## Question 1 

What is the distribution of pulse rates among students in 431 since 2014?

```{r}
surv15 |> tabyl(pulse) |> adorn_pct_formatting()
```

## Histogram, first try

```{r}
#| warning: true
ggplot(data = surv15, aes(x = pulse)) +
    geom_histogram(bins = 15, fill = "royalblue",  col = "seagreen1")
```

## Histogram (with warning suppressed)

```{r}
#| warning: false
ggplot(data = surv15, aes(x = pulse)) +
    geom_histogram(bins = 15, fill = "royalblue", col = "seagreen1")
```

## Some Key Numerical Summaries

```{r}
surv15 |> select(pulse) |> summary()
```

```{r}
length(surv15$pulse)
sd(surv15$pulse, na.rm = TRUE)
mad(surv15$pulse, na.rm = TRUE)
```

## Histogram, version 2

```{r}
dat1 <- surv15 |>
  filter(complete.cases(pulse))

ggplot(data = dat1, aes(x = pulse)) +
    geom_histogram(fill = "seagreen", col = "white", bins = 20) +
    labs(title = "Pulse Rates of Dr. Love's students",
         subtitle = "2014 - 2025",
         y = "Number of Students",
         x = "Pulse Rate (beats per minute)")
```

# Question 2

## Question 2

Does the distribution of student heights change over time?

```{r}
#| warning: true

ggplot(surv15, aes(x = year, y = height_in)) +
  geom_point(alpha = 0.7, color = "forestgreen")
```


## Yearly Five-Number Summaries

```{r}
surv15 |>
    filter(complete.cases(height_in)) |>
    group_by(year) |>
    summarize(n = n(), min = min(height_in), q25 = quantile(height_in, 0.25),
              median = median(height_in), q75 = quantile(height_in, 0.75),
              max = max(height_in))
```

## Boxplot of Heights by Year

```{r}
dat1 <- surv15 |>
    filter(complete.cases(height_in)) 

ggplot(data = dat1, aes(x = year, y = height_in)) +
    geom_boxplot() +
    labs(title = "Heights of Dr. Love's students, by year",
         subtitle = "2014 - 2025", x = "Year", y = "Height (in inches)")
```

## Adding a Violin to the Boxplot

```{r}
dat1 <- surv15 |>
    filter(complete.cases(height_in))

ggplot(data = dat1, aes(x = year, y = height_in)) +
    geom_violin() +
    geom_boxplot(aes(fill = year), width = 0.3) +
    guides(fill = "none") +
    scale_fill_viridis_d(alpha = 0.3) +
    labs(title = "Heights of Dr. Love's students, by year",
         subtitle = "2014 - 2025", x = "Year", y = "Height (in inches)")
```

## Key Numerical Summaries

```{r}
surv15 |>
    filter(complete.cases(height_in)) |>
    group_by(year) |>
    summarize(n = n(), mean = mean(height_in), sd = sd(height_in),
              median = median(height_in), mad = mad(height_in))
```

# Question 3

## Question 3 

Are the data on student heights in 2025 well described by a Normal distribution?

- Can we use a mean and standard deviation to describe the center and spread of the data effectively?

## Empirical Rule & 2025 Student Heights

```{r}
dat2 <- surv15 |>
  filter(complete.cases(height_in),
         year == "2025")

describe_distribution(dat2$height_in)
```

## Histogram of 2025 Student Heights

```{r}
dat2 <- surv15 |>
  filter(complete.cases(height_in)) |>
  filter(year == "2025")

ggplot(data = dat2, aes(x = height_in)) +
    geom_histogram(fill = "salmon", col = "white", binwidth = 2) +
    labs(title = "Heights of Dr. Love's students",
         subtitle = "2025 (n = 53 students with height data)",
         y = "Number of Students", x = "Height (inches)")
```

## Checking the 1-SD Empirical Rule

```{r}
surv15 |> filter(complete.cases(height_in)) |>
    filter(year == "2025") |>
    count(height_in >= 62.4 & height_in <= 69.7)

33/(33+20)
```

## 2-SD Empirical Rule

```{r}
surv15 |> filter(complete.cases(height_in)) |>
    filter(year == "2025") |>
    count(height_in >= 58.75 & height_in <= 73.35)

52/(52+1)
```

## 3-SD Empirical Rule

```{r}
surv15 |> filter(complete.cases(height_in)) |>
    filter(year == "2025") |>
    count(height_in >= 55.1 & height_in <= 77.0)

53/(53+0)
```

## Boxplots: Height & Haircut Price

```{r}
dat2 <- surv15 |> filter(complete.cases(height_in), year == "2025")

p2 <- ggplot(data = dat2, aes(x = "height (inches)", y = height_in)) +
  geom_violin() + geom_boxplot(width = 0.3, fill = "tomato") +
  labs(title = "Boxplot of 2025 Student Heights", x = "")

dat3 <- surv15 |> filter(complete.cases(haircut), year == "2025")

p3 <- ggplot(data = dat3, aes(x = "haircut ($)", y = haircut)) +
  geom_violin() + geom_boxplot(width = 0.3, fill = "dodgerblue") +
  labs(title = "Boxplot of 2025 Haircut Prices", x = "")

p2 + p3 + 
  plot_annotation(title = "2025 15-Question Survey Data")
```

# Session Information

```{r}
#| echo: true
xfun::session_info()
```
