---
title: "A First Quarto Template"
author: "Insert Your Name Here"
date: last-modified
format: 
  html:
    toc: true
    number-sections: true
    code-fold: show
    code-tools: true
    code-overflow: wrap
    embed-resources: true
    date-format: iso
    theme: default
---

## Load R Packages

```{r}
#| message: false

knitr::opts_chunk$set(comment = NA)

## add additional libraries/packages here, as needed
## leaving easystats then tidyverse as the last two packages loaded

library(easystats)
library(tidyverse)

theme_set(theme_bw()) 
```

## Load Dr. Love's R script

```{r}
## remove the ## before source below to load the `Love-431.R` script 
## from our 431-data web site and you want to include it in your work

## source("https://raw.githubusercontent.com/THOMASELOVE/431-data/refs/heads/main/data/Love-431.R")
```


## Load Data

```{r load_data}
## if you want to load in a data set called namebeta.csv
## and then create a tibble from it called namealpha
## then uncomment the next line by removing the #

# namealpha <- read_csv("namebeta.csv") 
```

# Big Section Header

## Subsection Header

When you click the **Render** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r}
iris |> summary()
```

# Building the Next Section

## Including Plots

You can also embed plots, for example:

```{r}
ggplot(data = iris, aes(x = Sepal.Length)) +
  geom_histogram(bins = 20, col = "white", fill = "blue")
```

# Session Information

```{r}
xfun::session_info()
```



