---
title: "431 Lab 1 Template (Replace this name)"
author: "(Your Name Goes Here)"
date: last-modified
format: 
  html:
    toc: true
    number-sections: true
    embed-resources: true
    date-format: iso
    theme: materia
---

:::{.callout-important}

Delete **all of the instructions** we provide to you in this template, in favor of your own words, before submitting your work. You are welcome to retain any or all of the R code we provide in this template as part of your response.

:::

## R Setup {.unnumbered}

```{r}
#| message: false

library(knitr)

## add additional packages here, as needed

library(easystats)
library(tidyverse)

## should you choose to use the Love-431.R script, source it in here...

```

# Task 1

Here is the heading of the data file, as shown in the instructions.

```{r}
cms_patient_experience |> head()
```

Here is an empty code chunk where you can put your code to obtain the desired numerical summaries.

```{r}

```


Write your complete English sentences here.

If you need a second paragraph, place it here, with a blank line between paragraphs.


# Task 2

Place your R code to fit the model here.

```{r}

```


Summarize your findings here, being sure to specify everything we ask for in the instructions.

# Task 3

Place your R code to build your plot here.

```{r}

```

Your interpretation of the plot should goes here.

# Task 4

Here is the code to create the subset of interest, from our instructions:

```{r}
task4dat <- cms_patient_experience |>
  filter(measure_cd == "CAHPS_GRP_2" | measure_cd == "CAHPS_GRP_8") |>
  pivot_wider(names_from = c(measure_cd, measure_title),
              values_from = prf_rate) |>
  rename("Communicate" = "CAHPS_GRP_2_CAHPS for MIPS SSM: How Well Providers Communicate",
         "Staff" = "CAHPS_GRP_8_CAHPS for MIPS SSM: Courteous and Helpful Office Staff") |>
  drop_na()

head(task4dat)
```



Next, place the R code you use to fit and display the relevant linear model in the code chunk below.

```{r}

```

Your interpretation of the model's slope and intercept should go here.

Here is the code for the plot shown in the instructions, which you will need to modify appropriately:

```{r}
ggplot(task4dat, aes(x = Staff, y = Communicate)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ x, se = TRUE, col = "red") +
  theme_bw()
```

Here is where you should put your comments about what you learn by comparing the blue and red smooths from your revised plot.

# Task 5

:::{.callout-tip title="Delete these instructions when submitting your work"}

This will be the video. No need to write anything substantial here. You just need to specify the name of the file, which should ideally be ...

`yourname-431lab1.mp4`

:::

# AI Usage

:::{.callout-tip title="Delete these instructions when submitting your work"}

All students should have an AI Usage section.

- If you decide to get help from a large language model (like ChatGPT) to help with your phrasing of ideas, or building code, OK, but you need to describe what you did in some detail here. Use multiple clear and complete sentences.
- If you use nothing outside of the spell-checker and code completion tools within RStudio, please write that here, as follows:

In preparing this response, I made no use of AI outside of spell-check and code completion within RStudio.

:::

# Session Information

:::{.callout-tip title="Delete these instructions when submitting your work"}

Use the code below to include your session information.

:::

```{r}
xfun::session_info()
```
