---
title: "431 Lab 2 Template (Replace this name)"
author: "(Your Name Goes Here)"
date: last-modified
format: 
  html:
    toc: true
    number-sections: true
    embed-resources: true
    date-format: iso
    theme: materia
---

:::{.callout-important}

Delete **all of the instructions** we provide to you in this template, in favor of your own words, before submitting your work. You are welcome to retain any or all of the R code we provide in this template as part of your response.

:::

## R Setup {.unnumbered}

```{r}
#| message: false

library(infer)
library(knitr)
library(patchwork)
library(rstanarm)

## add additional packages here, as needed

library(easystats)
library(tidyverse)

theme_set(theme_bw()) ## select whatever theme you like best

## should you choose to use the Love-431.R script, source it in here...

```

# Task 1

Prior to starting on any of the subtasks, you'll need to ingest the `lab2-task1.csv` file. Please take any necessary steps to ensure that unnecessary messages and warnings are dealt with before you submit this Lab for grading.

```{r}

```


## Task 1a

Here, you should add the column of paired differences (`prem_2020 - prem_2016` is the order we prefer) to the sample, then visualize and summarize (numerically) those paired differences.

```{r}

```

## Task 1b

Here you should run the three different estimation approaches discussed in the instructions, then build a small table of the results.

### Ordinary Least Squares

```{r}

```

### Bootstrap

```{r}
set.seed(4311)

```

### Bayesian linear model

Please use `refresh = 0` when fitting your model with `stan_glm()`.

```{r}
set.seed(4312)

```


### Summary Table of Findings

Method | Point Estimate | 95% CI
:--------: | :-------: | :---------:
OLS linear model | insert here | insert here
Bootstrap | insert here | insert here
Bayes linear model | insert here | insert here


## Task 1c

Write your two to four sentences here.

# Task 2

Prior to starting on any of the subtasks, you'll need to ingest the `lab2-task2.csv` file. Please take any necessary steps to ensure that unnecessary messages and warnings are dealt with before you submit this Lab for grading.

## Task 2a

Here you need to visualize and summarize the `vote2020` data within each `firearm_cat` group.

```{r}

```


## Task 2b

Here you should run the four different estimation approaches discussed in the instructions, then build a small table of the results.

### Ordinary Least Squares

```{r}

```


### Welch t procedure

```{r}

```

### Bootstrap

```{r}
set.seed(4313)

```

### Bayesian linear model

Please use `refresh = 0` when fitting your model with `stan_glm()`.

```{r}
set.seed(4314)

```


### Summary Table of Findings

Method | Point Estimate | 95% CI
:--------: | :-------: | :---------:
OLS linear model | insert here | insert here
Welch t | insert here | insert here
Bootstrap | insert here | insert here
Bayes linear model | insert here | insert here


## Task 2c

Write your two to four sentences here.



# Task 3

Write your response here.

If you need a second paragraph, separate it from the first with a blank line.

# AI Usage

Write your AI Usage section here following the instructions.

# Session Information

Use the code below to include your session information.

```{r}
xfun::session_info()
```